Poster Data Analysis

### 2018-09-11 notebooks/poster_analysis.Rmd
removed acrB from analysis

# ARIBA AMR gene results (megares database, for mutations in intrinsic genes)
megares_results <- read.table("../data/megares_results.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)

@@

species_data <- select(isolate_data, c(id, species))

total_data <- isolate_data %>%
  left_join(mic_data, by = "id") %>%
  left_join(mlst_results, by = "id") %>%
  rename("m_gyrB" = gyrB) %>%
  left_join(resfinder_results, by = "id") %>%
  select(-type) %>%
  left_join(megares_results, by = "id") %>%
  select(-type)
```

@@

### Percent mutations in intrinsic genes
```{r}
megares_results %>%
  select(-c(id, type, acrB)) %>%
  mutate(total = rowSums(., na.rm = TRUE),
         result = if_else(total != 0, 1, 0)) %>%
  group_by(result) %>%
  count() %>%
  ungroup() %>%
  mutate(result = if_else(result == 0, "Absent", "Present")) %>%
  spread(result, n) %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total * 100,2),
         lwr = round(get_binCI(Present, Total)[1], 2),
         upr = round(get_binCI(Present, Total)[2], 2))
```

@@

## Correlation plot for mutations in intrinsic genes
```{r}
corr_megares <- megares_results %>%
  select(-c(type, acrB)) %>%
  left_join(species_data, by = "id") %>%
  mutate(compl = complete.cases(.)) %>%
  filter(compl == TRUE) %>%
  split(., f = .$species) %>%
  lapply(., function(x) select(x, -c(species, id, compl)))

@@

micplot_data <- mic_data %>%
  select(id, CIP) %>%
  left_join(megares_results, by = "id") %>%
  left_join(resfinder_results, by = "id") %>%
  select(-c(acrB, type.x, type.y)) %>%
  mutate(compl = complete.cases(.)) %>%
  filter(compl == TRUE) %>%
  select_at(vars(id, CIP,selected_mut, selected_genes)) %>%
  mutate(none = if_else(rowSums(.[,3:ncol(.)]) != 0, 0, 1)) %>%
  group_by_at(vars(selected_mut, selected_genes, none)) %>%
  { mutate(ungroup(.), group = group_indices(.)) } %>%
  gather(gene, value, -c(id, CIP, group)) %>%
  mutate(gene = ifelse(value == 0 & gene != "none", NA, gene),
         value = ifelse(gene == "none" & value == 0, NA, value)) %>%
  na.omit()

@@

```{r message=FALSE, warning=FALSE}
mut_genes_list <- megares_results %>%
  left_join(isolate_data, by = "id") %>%
  gather(key, value, mut_names) %>%
  filter(key != "acrB") %>%
  group_by(key, value, species) %>%
  count() %>%
  ungroup() %>%
  mutate(value = if_else(value == 1, "Present", "Absent")) %>%
  spread(value, n, fill = 0) %>%
  select(key, species, Present, Absent) %>%
  split(f = .$key)

>>>>

# ARIBA AMR gene results (megares database, for mutations in intrinsic genes)
megares_results <- read.table("../data/megares_results.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F) %>%
  select(-acrB)

@@

species_data <- select(isolate_data, c(id, species))
```

@@

### Percent mutations in intrinsic genes
```{r}
megares_results %>%
  select(-c(id, type)) %>%
  mutate(total = rowSums(., na.rm = TRUE),
         result = if_else(total != 0, 1, 0)) %>%
  group_by(result) %>%
  count() %>%
  ungroup() %>%
  mutate(result = if_else(result == 0, "Absent", "Present")) %>%
  spread(result, n) %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total * 100,2),
         lwr = round(get_binCI(Present, Total)[1], 2),
         upr = round(get_binCI(Present, Total)[2], 2))
```

@@

## Correlation plot for mutations in intrinsic genes
```{r}
corr_megares <- megares_results %>%
  select(-type) %>%
  left_join(species_data, by = "id") %>%
  mutate(compl = complete.cases(.)) %>%
  filter(compl == TRUE) %>%
  split(., f = .$species) %>%
  lapply(., function(x) select(x, -c(species, id, compl)))

@@

micplot_data <- mic_data %>%
  select(id, CIP) %>%
  left_join(megares_results, by = "id") %>%
  left_join(resfinder_results, by = "id") %>%
  select(-c(type.x, type.y)) %>%
  mutate(compl = complete.cases(.)) %>%
  filter(compl == TRUE) %>%
  select_at(vars(id, CIP,selected_mut, selected_genes)) %>%
  mutate(none = if_else(rowSums(.[,3:ncol(.)]) != 0, 0, 1)) %>%
  group_by_at(vars(selected_mut, selected_genes, none)) %>%
  { mutate(ungroup(.), group = group_indices(.)) } %>%
  gather(gene, value, -c(id, CIP, group)) %>%
  mutate(gene = ifelse(value == 0 & gene != "none", NA, gene),
         value = ifelse(gene == "none" & value == 0, NA, value)) %>%
  na.omit()

@@

```{r message=FALSE, warning=FALSE}
mut_genes_list <- megares_results %>%
  left_join(isolate_data, by = "id") %>%
  gather(key, value, mut_names) %>%
  group_by(key, value, species) %>%
  count() %>%
  ungroup() %>%
  mutate(value = if_else(value == 1, "Present", "Absent")) %>%
  spread(value, n, fill = 0) %>%
  select(key, species, Present, Absent) %>%
  split(f = .$key)
